How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2021-09-27 analysis/paper/paper.Rmd
Change in 002 to knit RMD file

```{r volume-density, fig.cap="Artifact volumetric density over time. The size of data points represent the total number of artifacts from each assemblage and the colour indicates the presence of stemmed points. The inset plot shows direct comparison of artifact densities for assemblages with and without stemmed points.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/002-artifact-volumetric-density.R"))}
# quietly(source(here::here("analysis/paper/002-artifact-volumetric-density.R")))
knitr::include_graphics(here::here("analysis/figures/002-age-by-density.png"))
```

>>>>

```{r volume-density, fig.cap="Artifact volumetric density over time. The size of data points represent the total number of artifacts from each assemblage and the colour indicates the presence of stemmed points. The inset plot shows direct comparison of artifact densities for assemblages with and without stemmed points.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/002-artifact-volumetric-density.R"))}
quietly(source(here::here("analysis/paper/002-artifact-volumetric-density.R")))
knitr::include_graphics(here::here("analysis/figures/002-age-by-density.png"))
```
